BurgerTown Presents: Open Adcess

### 2017-04-29 digital-library.tex
Update digital-library.tex

Lastly, we are working on a proposal that will greatly reduce ACM hosting
costs, namely we  will replace the only real download button with a fake one.

@@

Simple. Once a quarter, the Ricketts family convokes Gary Cohn, Dennis Rodman,
Colonel Sanders, and the rest of the Economic Advisory Council at Chicago's
historic Wrigley Field to make use of the stadium's native Noiseometer. As Pat
Hughes reads the papers over the PA , the council---taking especial care to
note the presence of key phrases like ``cross-promotional deal mechanics
revenue streams jargon synergy" and ``a strategic planning initiative\ldots
with a focus on strategic dynamism"---emits cheers in proportion to its
perception of the paper's impact, and these cheers are registered on the
Noiseometer, which assigns metrics of impact to each paper, as shown in Figure~\ref{fig:noiseometer}

>>>>

Lastly, we are working on a proposal that will greatly reduce ACM hosting
costs; namely, we  will replace the only real download button with a fake one.

@@

Simple. Once a quarter, the Ricketts family convokes Gary Cohn, Dennis Rodman,
Colonel Sanders, and the rest of the Economic Advisory Council at Chicago's
historic Wrigley Field to make use of the stadium's native Noiseometer. As Pat
Hughes reads the papers over the PA, the council---taking especial care to
note the presence of key phrases like ``cross-promotional deal mechanics
revenue streams jargon synergy" and ``a strategic planning initiative\ldots
with a focus on strategic dynamism"---emits cheers in proportion to its
perception of the paper's impact, and these cheers are registered on the
Noiseometer, which assigns metrics of impact to each paper, as shown in Figure~\ref{fig:noiseometer}
